Simulation of Congenital Heart Defect Corrective Surgeries Using Thin Shell Elements

### 2012-03-02 Doc/Miccai/shell-model.tex
small fixes
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@384 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

Options on the choice of model are limited. Mass-spring models, often used for cloth simulation \cite{Volino2005b}, allow for fast computation but do not do not posses the required level of physical accuracy and therefore are inappropriate for predictive simulations. On the contrary, simulation models based on the formulation of finite elements, either 3-dimensional elements or thin shell elements, are commonly used when high physical accuracy is required but are well known to be computationally expensive. The hybrid blood vessel model of \cite{Li2009} strikes a balance but is too constrained to be used as a truly universal approach for all kinds of surgical procedures used in CHD corrective surgery. We propose a model based on thin shell elements that still allows for fast computation with a reasonable number of elements.

\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.4\columnwidth]{img/shell.pdf}
  \caption{Shell element combines bending with in-plane deformations}
  \label{fig-shell}
\end{figure}

>>>>

Options on the choice of model are limited. Mass-spring models, often used for cloth simulation \cite{Volino2005b}, allow for fast computation but do not posses the required level of physical accuracy and therefore are inappropriate for predictive simulations. On the contrary, simulation models based on the formulation of finite elements, either 3-dimensional elements or thin shell elements, are commonly used when high physical accuracy is required but are well known to be computationally expensive. The hybrid blood vessel model of \cite{Li2009} strikes a balance but is too constrained to be used as a truly universal approach for all kinds of surgical procedures used in CHD corrective surgery. We propose a model based on thin shell elements that still allows for fast computation with a reasonable number of elements.

\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.4\columnwidth]{img/shell.pdf}
  \caption{Shell element combines bending with in-plane deformations.}
  \label{fig-shell}
\end{figure}
